VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-18 snapshot_system/paper_background.tex
re
change bk

Another disadvantage of cross-VM sharing is that it complicates 
snapshot deletion, 
which occurs frequently when snapshots expire regularly. 
The mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  is effective for
deletion, but still carries a significant cost, especially in a distributed 
setting.
%to count if a data chunk is still shared by other snapshots.

>>>>

Another disadvantage of cross-VM sharing is that it complicates 
snapshot deletion, 
which occurs frequently when snapshots expire regularly. 
Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
the dependencies from data containers to metadata groups, such that only a subset of
metadata needs to be scanned in order to reclaim the garbage in a given data container.
However, data in VM environment tend to be highly dedupable which means
such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost.

% especially in a distributed setting.
%to count if a data chunk is still shared by other snapshots.
